Models

### 2024-11-15 analysis/05_model_metrics.Rmd
Fix protected area models

log_mods <- tibble(metric_name = log_metrics, 
                         base = "log(value) ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "log(value) ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "log(value) ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "log(value) ~ year_scaled * climate + (year_scaled|study_id/rarefyID)",
                   protected_area = "value ~ year_scaled * protected_area + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate, protected_area), names_to = "model_id", values_to = "formula")

logone_mods <- tibble(metric_name = logone_metrics, 
                         base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "logvalue ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "logvalue ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "logvalue ~ year_scaled * climate + (year_scaled|study_id/rarefyID)",
                      protected_area = "value ~ year_scaled * protected_area + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate, protected_area), names_to = "model_id", values_to = "formula")

>>>>

log_mods <- tibble(metric_name = log_metrics, 
                         base = "log(value) ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "log(value) ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "log(value) ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "log(value) ~ year_scaled * climate + (year_scaled|study_id/rarefyID)",
                   protected_area = "log(value) ~ year_scaled * protected_area + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate, protected_area), names_to = "model_id", values_to = "formula")

logone_mods <- tibble(metric_name = logone_metrics, 
                         base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "logvalue ~ year_scaled * taxa + (year_scaled|study_id/rarefyID)",
                         realm = "logvalue ~ year_scaled * realm + (year_scaled|study_id/rarefyID)",
                         climate = "logvalue ~ year_scaled * climate + (year_scaled|study_id/rarefyID)",
                      protected_area = "logvalue ~ year_scaled * protected_area + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate, protected_area), names_to = "model_id", values_to = "formula")
